# Text analysis

```{r}
require(quanteda)
options(width = 110)
require(readtext)
library(tidyverse)
require(quanteda.textstats)
require(quanteda.textplots)
fdata_sub <- read_csv("data/12k/fdata_sub.csv")
library(knitr)
```

## Ngram analysis in Quanteda


### Creating the corpus object

Sample of corpus
```{r}
corp <- corpus(fdata_sub, text_field = "abstract")

glimpse(docvars(corp))
```



### Creating the tokens object

Head (first bigrams)

```{r}
toks <- tokens(corp, remove_punct = TRUE)

toks_nostop <- tokens_select(toks, pattern = stopwords("en"), selection = "remove")

toks_ngram <- tokens_ngrams(toks_nostop, n = 2)

head(toks_ngram[[1]], 5)
```


### Creating the document feature matrix

```{r}
dfm <- dfm(toks_ngram)
topfeatures(dfm)
```



In abstracts, raw counts by year:

* "climate_change"
* "global_warming"
* "climate_crisis"

```{r}

# Get frequency grouped by year
freq_grouped <- textstat_frequency(dfm(toks_ngram), 
                                   groups = publication_year)



# Filter the term "climate"
freq_climate_change <- subset(freq_grouped, freq_grouped$feature %in% "climate_change")  

freq_global_warming <- subset(freq_grouped, freq_grouped$feature %in% "global_warming")

freq_climate_crisis <- subset(freq_grouped, freq_grouped$feature %in% "climate_crisis")


bound_frames <- rbind(
      freq_global_warming,
      freq_climate_change,
      freq_climate_crisis)

fig01 <- ggplot(bound_frames %>% filter(group != "2023"), aes(x = as.numeric(group), y = frequency, color = feature)) +
    geom_point() + 
    geom_line() +
    scale_y_continuous() +
    xlab(NULL) + 
    ylab("Frequency") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   theme_minimal() +
  labs(title = "Phraseology, emerging")

fig01
```

## Climate Frames

Proportion of phrase: counts divided by sum of target phrases in year

```{r}
# Get frequency grouped by year
freq_grouped <- textstat_frequency(dfm(toks_ngram), 
                                   groups = publication_year)



# Filter the term "climate"
freq_climate_change <- subset(freq_grouped, freq_grouped$feature %in% "climate_change")  

freq_global_warming <- subset(freq_grouped, freq_grouped$feature %in% "global_warming")

freq_climate_crisis <- subset(freq_grouped, freq_grouped$feature %in% "climate_crisis")


bound_frames <- rbind(
      freq_global_warming,
      freq_climate_change,
      freq_climate_crisis) %>%
  group_by(group) %>%
  mutate(prop = frequency/sum(frequency)) %>%
  ungroup()

fig02 <- ggplot(bound_frames %>% filter(group != "2023") , aes(x = as.numeric(group), y = prop, color = feature)) +
    geom_point() + 
    geom_line() +
    scale_y_continuous() +
    xlab(NULL) + 
    ylab("Frequency") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   theme_minimal()

fig02
```

## Phrases of interest

Key phrases, grouped loosely:

Equity and justice

* climate justice
* environmental justice
* environmental equity
* climate equity
* environmental equity
* climate equity

Consensus and denial

* scientific consensus
* climate denial
* climate skepticism

```{r}

freq_climate_action <- subset(freq_grouped, freq_grouped$feature %in% "climate_action")

# equity and justice frame

freq_climate_justice <- subset(freq_grouped, freq_grouped$feature %in% "climate_justice")

freq_enviro_justice <- subset(freq_grouped, freq_grouped$feature %in% "environmental_justice")

freq_env_equity <- subset(freq_grouped, freq_grouped$feature %in% "environmental_equity")

freq_clim_equity <- subset(freq_grouped, freq_grouped$feature %in% "climate_equity")

freq_climate_adaptation <- subset(freq_grouped, freq_grouped$feature %in% "climate_adaptation")

# consensus, denial

freq_sci_consensus <- subset(freq_grouped, freq_grouped$feature %in% "scientific_consensus")

freq_climate_denial <- subset(freq_grouped, freq_grouped$feature %in% "climate_denial")

freq_climate_skepticism <- subset(freq_grouped, freq_grouped$feature %in% "climate_skepticism")


# bind above

bound_something <- rbind(
      freq_climate_denial,
      freq_climate_skepticism,
      freq_climate_action,
      freq_climate_justice,
      freq_enviro_justice,
      freq_climate_adaptation,
      freq_sci_consensus,
      freq_env_equity,
      freq_clim_equity
      )

fig03 <- ggplot(bound_something %>% filter(group != "2023"), aes(x = as.numeric(group), y = frequency, color = feature)) +
    geom_point() + 
    geom_line() +
    scale_y_continuous() +
    xlab(NULL) + 
    ylab("Frequency") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme_minimal() +
  labs(title = "Bigrams of interest, over time")

fig03
```

```{r}
fig04 <- ggplot(bound_something %>% filter(group != "2023"), aes(x = as.numeric(group), y = frequency, color = feature)) +
    geom_smooth(se=F) +
    scale_y_continuous() +
    xlab(NULL) + 
    ylab("Frequency") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme_minimal() +
  labs(title = "bigrams of interest, over time (smoothed)")

fig04
```


As a proportion...

```{r}
bound_st_prop <- bound_something %>%
  group_by(feature) %>%
  mutate(prop2 = frequency/sum(frequency)) %>%
  ungroup()

fig05 <- ggplot(bound_st_prop %>% filter(group != "2023"), aes(x = as.numeric(group), y = prop2, color = feature)) +
    geom_point() + 
    geom_line() +
    scale_y_continuous() +
    xlab(NULL) + 
    ylab("proportion of bigrams of interest") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme_minimal() +
  labs(title = "bigrams of interest, as a proportion of total")

fig05
```
Grouped

* Belief = climate skepticism, climate denial, scientific consensus
* Equity = climate justice, environmental justice, climate equity, environmental equity
* Response = climate action, climate adaptation

```{r}
group_frame <- bound_something %>%
  mutate(feature_2 = ifelse(feature %in% c("climate_action", "climate_adaptation"), "climate_response", 
                            ifelse(feature %in% c("climate_skeptism", "climate_denial", "scientific_consensus"), "climate_belief", 
                                   "climate_equity")))

fig06 <- ggplot(group_frame %>% filter(group != "2023"), aes(x = as.numeric(group), y = frequency, color = feature_2)) +
    geom_smooth(se=F) +
    scale_y_continuous() +
    xlab(NULL) + 
    ylab("Group frequency") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme_minimal() +
  labs(title = "Shifting foci: \nIs it real? Who will it affect? What do we do? ",
       subtitle = "grouped bigrams as frames")

fig06
```


```{r}
group_frame_prop <- bound_st_prop %>%
  mutate(feature_2 = ifelse(feature %in% c("climate_action", "climate_adaptation"), "climate_response", 
                            ifelse(feature %in% c("climate_skeptism", "climate_denial", "scientific_consensus"), "climate_belief", 
                                   "climate_equity")))%>%
  group_by(feature_2) %>%
  mutate(prop2 = frequency/sum(frequency)) %>%
  ungroup()

fig07 <- ggplot(group_frame_prop %>% filter(group != "2023"), aes(x = as.numeric(group), y = prop2, color = feature_2)) +
    geom_smooth(se=F) +
    scale_y_continuous() +
    xlab(NULL) + 
    ylab("Proportion of Sum") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Shifting foci: \nIs it real? Who will it affect? What do we do? ") +
  theme_minimal()

fig07

```

## Outputs

```{r, include=FALSE}
fig01 
fig02
fig03
fig04
fig05
fig06
fig07
```

